Future Virtual Particle Method for Pedestrian Navigation

### 2015-03-15 doc/informe/paper/main.tex
actualizo las imagenes del informe. ahora el informe ya no tiene mas formato paper. elimino arhcivos temporales.

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{graphicx}

\makeatletter

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

\usepackage{babel}

\makeatother

\usepackage{babel}
\begin{document}

@@

\author{
  Castiglione, Gonzalo\\
  \texttt{gcastigl@gmail.com}
  \and
  Marseillan, Agustin\\
  \texttt{agustinmarseillan@gmail.com}
  \and
  Parisi, Daniel\\
  \texttt{danielparisi@xxxxx.com}
}
\date{}

\maketitle

\vspace{10cm}
\begin{center}
    \includegraphics[scale=0.08]{pics/ITBA}
    \par
\end{center}

\pagebreak{}

\begin{abstract}
Pedestrians are modeled as passive objects affected by repulsive and
attractive forces in the Social Force Model (SFM). This force governed
model leads to unnatural behaviors that don't resemble reality. This
paper presents an avoidance collision method based in pedestrian self
governed decisions, by calculating the position of every pedestrian
in the future, a given pedestrian can adjust his velocity vector to
avoid collisions instead of a repulsive force.

\textbf{keywords:} pedestrian, collision avoidance, future virtual
particle, force model.
\end{abstract}

\section{Introduction}

\subsection{Motivation and previous work}

@@

A famous example of continuous and force based model is the Social
Force Model \cite{key-helb1995,key-helb2000}. In this model the dynamic
for virtual pedestrians is derived from the Newton equation's considering
the total force exerted over each agent is the result of three forces:
Contact, Social and Driving Force. While the driving force points
towards the final objective of each pedestrian, the social force is
repulsive and acts as a kind of collision avoidance force. However
this social force term introduces several artifices in some configurations.
See for example Lakoba \cite{key-tara2005}, Parisi \cite{key-pari2009}.

@@

\begin{figure}[h]
\begin{centering}
\includegraphics[scale=0.4]{pics/sfm/drivingforce} 
\par\end{centering}

\caption{\label{fig:driving-force}Driving force}
\end{figure}

@@

\begin{figure}[h]
\begin{centering}
\includegraphics[scale=0.4]{pics/sfm/sf} 
\par\end{centering}

\caption{Social Force\label{fig:Social-Force}}
\end{figure}

@@

$g$ is $0$ if $\epsilon_{ij}\leq0$ or $\epsilon_{ij}$ otherwise\\

@@

\begin{figure}[h]
\begin{centering}
\includegraphics[scale=0.4]{pics/sfm/ganular} 
\par\end{centering}

\caption{Colliding pedestrians\label{fig:colliding-pedestrians}}
\end{figure}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline 
Name  & Value\tabularnewline
\hline 
\hline 
$A$  & $2000\,[N]$\tabularnewline
\hline 
$B$  & $0.08\,[m]$\tabularnewline
\hline 
$k_{n}$  & $1.2\,10^{5}\,[\frac{N}{m}]$\tabularnewline
\hline 
$k_{t}$  & $2.4\,10^{5}\,[\frac{kg}{m/s}]$\tabularnewline
\hline 
$\tau$  & $0.5\,[s]$\tabularnewline
\hline 
\end{tabular}
\par\end{center}

@@

Given that the SFM adds a fictional force on pedestrians, navigation
is unnatural and doesn't resemble reality. SFM isn't validated using
well known metrics for real-case scenarios such as the flow of pedestrians
going out a door and the fundamental diagram \cite{key-pari2009}.

In the FVPM, the social force in equation \ref{eq:driving-force}
is eliminated and replaced with a dynamic driving force towards a
short term objective, which is equal to equation \ref{eq:desired-direction}
replacing $\vec{x}_{i}^{k}$ with $\vec{x_{i'}}$, where $\vec{x_{i'}}$
is an estimation of the location of pedestrian $i$ in the near future.
$i'$ will be called Future Virtual Particle.

AGREGADO POR PARISI: LLEGAMOS A POSTULAR ESTE MODELO DESPUES DE VARIOS CICLOS DE ITERACIONES Y NUMEROSAS PRUEBAS DE DE VARIANTES HASTA CONVERGER AL MODELO PRESENTADO QUE MODELA ADECUADAMENTE VARIAS SITUACIONES

@@

A pedestrian is defined as follows:

\begin{itemize}
    \item Circular shape

@@

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.4]{pics/pedestrian-top} 
    \caption{\label{fig:pedestrian-geometry}Illustration of pedestrian $i$ and its FVP ($i'$).}
\end{figure}

@@

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.4]{pics/geometry}
    \caption{\label{fig:pedestrian-vectors}Vectorial definitions}
\end{figure}

@@

\subsubsection{Force calculation}

\begin{itemize}
\item Dynamic of the FVP

Each pedestrian has to reach the long term objective at some point,
to ensure this, the FVP needs to be aligned with the shortest path
to the long term objective $\mathbf{x_{o}}$. On the other hand, there
are sometimes obstacles in the way, which will make this impossible,
in this cases, the route will have to change depending on the situation.

To model this situations, two types of forces act over the FVP: 
\begin{itemize}
\item Internal force \\

@@

The second spring starts on $x_{i'}$ and ends on $x_{i}+RD\frac{\vec{x_{i}x_{o}}}{\mid\vec{x_{i}x_{o}}\mid}$
with a spring constant $K_{1}$. This spring represents the pedestrian's
desire to reach his target. A greater spring constant will force a
straighter path. In order to avoid an oscillatory movement, a damping
$\gamma$ was added to the spring.\\

@@

\begin{equation}
    F_{internal}(i)=F_{S1}(i)+F_{S2}(i)
\end{equation}

@@

\[
    F_{S1}(i)=K_{1}\cdot(|\vec{r}|-RD)\cdot\hat{r}
\]
\[
    F_{S2}(i)=\, K_{2}(\theta_{i})\cdot(\vec{x_{i'}}-(\vec{x_{i}}+\hat{x_{i}o}\cdot RD))
\]

\begin{figure}[h]
    \centering{}\includegraphics[scale=0.35]{pics/pedestrian-internal-forces}
    \caption{Pedestrian internal forces}
\end{figure}

\item Avoidance forces \\
 This force will produce avoidance movements when obstacles are detected
on the path. The magnitude of this force is calculated using two factors:
\\
 The first factor is calculated for each of the pedestrian $j$ ($j\neq i$)
who is in the range of sight of pedestrian $i$. This restriction
is verified using the following condition:

\[
    \mathbf{r_{ii'}}\bullet\mathbf{r_{ij}}<0
\]

@@

\[
    F_{ext}(i')=FF(i')+FP(i')+FW(i')
\]
where 
\[
    FF_{(}i')=\sum_{j}(\alpha_{ff}e^{-s/\beta_{ff}})
\]
\[
    FP_{(}i')=\sum_{j}(\alpha_{fp}e^{-t/\beta_{fp}})
\]
\[
    FW_{(}i')=\sum_{w}(\alpha_{fw}e^{-dist(w,i')/\beta_{fw}})
\]

@@

@@

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.4]{pics/pedestrian-top-forces}
    \caption{\label{fig:External-forces-affecting}External forces affecting future$i'$}
\end{figure}

@@

To avoid high symetry situations, a low noise $P=10\%$ is added to
$F$. There are two ways to apply this noise: 
\begin{itemize}

\item Radial noise:

@@

    \begin{itemize}
        \item A value $sgn=\{-1,\,1\}$ is taken randomly from a uniform distribution
        and a value $p$ from $[-P,\, P]$. Then \\
        \[
            M=\left(\begin{array}{cc}
            \cos(\pi*sgn) & -\sin(\pi*sgn)\\
            \sin(\pi*sgn) & \cos(\pi*sgn)
            \end{array}\right)
        \]
        \[
            FA_{i'}=F_{i'}*p*M
        \]
    \end{itemize}
\end{itemize}

At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply movement
equations.
\end{itemize}
\item Dynamic of the pedestrian

@@

The results where compared to the SFM model \cite{key-helb2000}.
The test scenarios where crossing and hallway for they present the
main types of symmetry (90 degrees and 180 degrees respectively). \\

Hallway scenario: A $15[m]$ by $4[m]$ hallway. Pedestrians are generated
from each end at a pace of 1 pedestrian per second with the other
end as target. \\
 This scenario is shown in figure \ref{fig:hallway-scenario}.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.35]{pics/scenarios/hallway}
    \caption{\label{fig:hallway-scenario}Hallway Scenario}
\end{figure}

Crossing scenario: Two hallways of $25[m]$ lenght by $5[m]$ width
put toghether in the center forming a cross. Pedestrians are generated
from the top, targeting the bottom, and from the right end, targeting
the left end, at a pace of 1 pedestrian per second. \\
 This scenario is shown in figure \ref{fig:cross-scenario}.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.3]{pics/scenarios/cross}
    \caption{\label{fig:cross-scenario}Cross Scenario}
\end{figure}

The metrics used to validate and verify the model against the defined
two previous scenarios are defined as follows:
\begin{enumerate}
\item Number of collisions: The equation for this metric is defined as:
\\

\begin{eqnarray*}
    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\wedge\\
    x_{i,t_{n-1}}-x_{j,t_{n-1}}>R_{i}+R_{j}\}\,\,\forall t_{n}
\end{eqnarray*}

\item Amount of collitions per instant: The equation for this metric is
defined as: \\

\begin{eqnarray*}
    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\}\,\,\forall t_{n}
\end{eqnarray*}

\item Average walking speed: The equation for this metric is defined as:
\\

\begin{eqnarray*}
    \sum v_{i,t_{n}}/\#\{i_{t_{n}}\}\,\,\forall t_{n}
\end{eqnarray*}

\item Average travel time: The average time that a pedestrian needed until
it reached the goal. The equation for this metric is defined as: \\

\begin{eqnarray*}
\sum\#\{i_{t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

\item Average travel distance: The average distance that a pedestrian traveled
until it reached the goal. The equation for this metric is defined
as: \\

\begin{eqnarray*}
\sum\#\{v_{i,t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

\item Average turn angle: The average angle turned by a pedestrian until
it reached the goal.\\

\begin{eqnarray*}
    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

\end{enumerate}
Escape room: A $20x20[m]$ room with a single $1.2[m]$ exit door
centered at the bottom. At the beginning, $100$ pedestrians are distributed
across the room and target the exit. When the first pedestrians exits
the room, a counter starts, and when the last one croses, it stops.
This way we can measure the flow of pedestrians leaving a room, which
is known to be between $0.69$ and $1$ for pedestrians without emergencies
\cite{key-pedEvDyn2012}. \\
 This scenario is shown in figure \ref{fig:room}.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.3]{pics/scenarios/room}
    \caption{\label{fig:room}Room Scenario}
\end{figure}

The metrics used where: 
\begin{enumerate}
    \item Escape flow: 
    \begin{eqnarray*}
    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

@@

\begin{itemize}
    \item Pedestrian

    \begin{itemize}
        \item $K_{1}=100$ {[}N/m{]}, 
        \item $\gamma=10$ 
        \item $K_{2}=150$ {[}N/m{]} 
    \end{itemize}
    \item FVP-FVP interaction

    \begin{itemize}
        \item $\alpha=1000$ 
        \item $\beta=[0.4,\,0.5]$ (Uniform distribution) 
        \end{itemize}
    \item Pedestrian-FVP interaction

    \begin{itemize}
        \item $\alpha=1000$ 
        \item $\beta=0.1$ 
    \end{itemize}
    \item FVP-Wall interaction

    \begin{itemize}
        \item $\alpha=10000$ 
        \item $\beta=0.1$ 
    \end{itemize}
\end{itemize}

@@

\begin{tabular}{|c|c|c|}
    \hline 
    Metric  & {\scriptsize{FVPM}} & {\scriptsize{SFM ($\alpha=2000,\,\beta=0.08$)}}\tabularnewline
    \hline 
    \hline 
    $1$  & {\scriptsize{$1.800\pm20.748$}} & {\scriptsize{$5.333\pm2.625$}}\tabularnewline
    \hline 
    $2$  & {\scriptsize{$34.600\pm8.333$}} & {\scriptsize{$12.333\pm8.340$}}\tabularnewline
    \hline 
    $3$  & {\scriptsize{$1.024\pm0.016$ $[m/s]$}} & {\scriptsize{$1.052\pm0.003$ $[m/s]$}}\tabularnewline
    \hline 
    $4$  & {\scriptsize{$1.910\pm0.022$ $[s]$}} & {\scriptsize{$1.876\pm0.003$ $[s]$}}\tabularnewline
    \hline 
    $5$  & {\scriptsize{$2.392\pm0.005$ $[m]$}} & {\scriptsize{$2.391\pm0.002$ $[m]$}}\tabularnewline
    \hline 
    $6$  & {\scriptsize{$91.062\pm12.122$ $[rad]$}} & {\scriptsize{$106.185\pm13.778$ $[rad]$}}\tabularnewline
    \hline 
\end{tabular}

@@

\begin{figure}[h]
    \begin{centering}
    \includegraphics[width=6cm]{pics/program/crossing-no-future} 
    \par\end{centering}
    \caption{\label{fig:crossing-no-future}Crossing visualization}
\end{figure}

\begin{figure}[h]
    \centering{} \includegraphics[width=6cm]{pics/program/crossing-future}
    \caption{\label{fig:crossing-future}Crossing visualization with visible future}
\end{figure}

@@

\newpage{}
\begin{thebibliography}{10}

\bibitem{key-hoog2004} Hoogonen and Bovy (2004).

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
% conference
\documentclass[draftclsnofoot]{IEEEtran}
\usepackage{graphicx}
% Add the compsoc option for Computer Society conferences.

% Sin esto los captions no aparecen centrados, no se porque!!!
\usepackage{caption}

% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

@@

\author{
    \IEEEauthorblockN{Castiglione Gonzalo,}
    \IEEEauthorblockA{Instituto Tecnológico de Buenos Aires\\
    }
    \and
    \IEEEauthorblockN{Marseillan Agustin,}
    \IEEEauthorblockA{Instituto Tecnológico de Buenos Aires\\
    }
    \and
    \IEEEauthorblockN{Parisi Daniel,}
    \IEEEauthorblockA{Instituto Tecnológico de Buenos Aires\\
    }
}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
Pedestrians are modeled as passive objects affected by repulsive and attractive forces in the Social Force Model (SFM). This force governed model leads to unnatural behaviors that don't resemble reality.
This paper presents an avoidance collision method based in pedestrian self governed decisions, by calculating the position of every pedestrian in the future, a given pedestrian can adjust his velocity vector to avoid collisions instead of a repulsive force.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
pedestrian, collision avoidance, future virtual particle, force model
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
\subsection{Motivation and previous work}

@@

A famous example of continuous and force based model is the Social
Force Model \cite{key-helb1995, key-helb2000}. In this model the dynamic for
virtual pedestrians is derived from the Newton equation's considering
the total force exerted over each agent is the result of three forces:
Contact, Social and Driving Force. While the driving force points
towards the final objective of each pedestrian, the social force is
repulsive and acts as a kind of collision avoidance force. However
this social force term introduces several artifices in some configurations.
See for example Lakoba \cite{key-tara2005}, Parisi \cite{key-pari2009}.

@@

\begin{figure}[h]
    \begin{centering}
    \includegraphics[scale=0.4]{pics/sfm/drivingforce} 
    \par
    \end{centering}
    \caption{\label{fig:driving-force}Driving force}
\end{figure}

@@

\begin{figure}[h]
    \begin{centering}
    \includegraphics[scale=0.4]{pics/sfm/sf} 
    \par
    \end{centering}
    \caption{Social Force\label{fig:Social-Force}}
\end{figure}

@@

$g$ is $0$ if $\epsilon_{ij} \leq 0$  or $\epsilon_{ij}$ otherwise\\

@@

\begin{figure}[h]
    \begin{centering}
    \includegraphics[scale=0.4]{pics/sfm/ganular} 
    \par\end{centering}
    \caption{Colliding pedestrians\label{fig:colliding-pedestrians}}
\end{figure}

@@

\begin{center}
    \begin{tabular}{|c|c|}
    \hline 
    Name & Value\tabularnewline
    \hline 
    \hline 
    $A$ & $2000\,[N]$\tabularnewline
    \hline 
    $B$ & $0.08\,[m]$\tabularnewline
    \hline 
    $k_{n}$ & $1.2\,10^{5}\,[\frac{N}{m}]$\tabularnewline
    \hline 
    $k_{t}$ & $2.4\,10^{5}\,[\frac{kg}{m/s}]$\tabularnewline
    \hline 
    $\tau$ & $0.5\,[s]$\tabularnewline
    \hline 
    \end{tabular}
    \par
\end{center}

@@

Given that the SFM adds a fictional force on pedestrians, navigation is unnatural and doesn't resemble reality.
SFM isn't validated using well known metrics for real-case scenarios
such as the flow of pedestrians going out a door and the fundamental diagram {Parisi et al. 2009}.

In the FVPM, the social force in equation \ref{eq:driving-force} is eliminated and replaced with a dynamic driving force towards a short term objective, which is equal to \ref{eq:desired-direction} replacing $\vec{x}_{i}^{k}$ with $\vec{x_{i'}}$, where $\vec{x_{i'}}$ is an estimation of the location 
of pedestrian $i$ in the near future. $i'$ will bbe called Future Virtual Particle.

@@

A pedestrian is defined as follows: 
\begin{itemize}

    \item Circular shape

@@

\begin{figure}[!ht]
    \centering{}
    \includegraphics[scale=0.4]{pics/pedestrian-top}
    \caption{\label{fig:pedestrian-geometry}Illustration of pedestrian $i$ and its FVP ($i'$).}
\end{figure}

@@

\begin{figure}[!ht]
    \centering{}
    \includegraphics[scale=0.4]{pics/geometry}
    \caption{\label{fig:pedestrian-vectors}Vectorial definitions}
\end{figure}

@@

\subsubsection{Force calculation}
\begin{itemize}
\item Dynamic of the FVP

Each pedestrian has to reach the long term objective at some point,
to ensure this, the FVP needs to be aligned with the shortest path
to the long term objective $\mathbf{x_o}$. On the other hand, there
are sometimes obstacles in the way, which will make this impossible,
in this cases, the route will have to change depending on the situation.

To model this situations, two types of forces act over the FVP:
\begin{itemize}

    \item Internal force \\

@@

    The second spring starts on $x_{i'}$ and ends on 
    $x_i + RD \frac{\vec{x_{i}x_{o}}}{\mid \vec{x_{i}x_{o}} \mid}$
    with a spring constant $K_{1}$.
    This spring represents the pedestrian's desire to reach his
    target. A greater spring constant will force a straighter path.
    In order to avoid an oscillatory movement,
    a damping $\gamma$ was added to the spring.\\

@@

    \begin{equation}
        F_{internal}(i)= F_{S1}(i) + F_{S2}(i)
    \end{equation}

@@

    \[
        F_{S1}(i) = K_{1} \cdot (|\vec{r}|-RD) \cdot \hat{r}
    \]
    \[
        F_{S2}(i) = \,K_{2}(\theta_{i}) \cdot (\vec{x_{i'}}-(\vec{x_{i}}+\hat{x_{i}o}\cdot RD))
    \]

    \begin{figure}[h]
        \centering{}
        \includegraphics[scale=0.35]{pics/pedestrian-internal-forces}
        \caption{Pedestrian internal forces}
    \end{figure}

    \item Avoidance forces \\
    \\
    This force will produce avoidance movements when obstacles are detected
    on the path. The magnitude of this force is calculated using two factors:
    \\
    The first factor is calculated for each of the pedestrian $j$ ($j\neq i$)
    who is in the range of sight of pedestrian $i$. This restriction
    is verified using the following condition:

    \[
        \mathbf{r_{ii'}}\bullet\mathbf{r_{ij}} < 0
    \]

@@

    \[
        F_{ext}(i') = FF(i') + FP(i') + FW(i')
    \]
    where
    \[
        FF_(i') = \sum_{j}(\alpha_{ff}e^{-s/\beta_{ff}})
    \]
    \[
        FP_(i') = \sum_{j}(\alpha_{fp}e^{-t/\beta_{fp}})
    \]
    \[
        FW_(i') = \sum_{w}(\alpha_{fw}e^{-dist(w,i')/\beta_{fw}})
    \]

@@

    \iffalse The first term of the sum represents the fact that $i$
    does not want to be in the same location as $j$ in the near future.
    Note that $j'$ represents the predicted location of $j$ inferred
    by another pedestrian (in this case, $i$) and because of this, it
    moves it's near future away of that predicted location. The second
    term, represents the same fact but taking in mind the current location
    of the pedestrian $j$. The same law applies to each of the walls
    on the simulation, the difference is that the closest point on the
    wall and and the future has to be calculated before applying the formula.
    Also, the constants $\alpha_{fw}$ and $\beta_{fw}$ have different
    values. \fi

@@

    \begin{figure}[!ht]
        \centering{}
        \includegraphics[scale=0.4]{pics/pedestrian-top-forces}
        \caption{\label{fig:External-forces-affecting}External forces affecting future $i'$}
    \end{figure}

@@

To avoid high symetry situations, a low noise $P=10\%$ is added to
$F$. There are two ways to apply this noise: 
\begin{itemize}
\item Radial noise:

@@

\begin{itemize}
\item A value $sgn=\{-1,\,1\}$ is taken randomly from a uniform distribution
and a value $p$ from $[-P,\, P]$. Then $FA_{i'}=rotation(F_{i'},\,\pi*sgn)*p$
is calculated. 
\end{itemize}
\end{itemize}

At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply movement
equations.

\end{itemize}
\item Dynamic of the pedestrian

@@

The results where compared to the SFM \cite{key-helb2000}. The test scenarios
where crossing and hallway for they present the main types of symmetry
(90 degrees and 180 degrees respectively).

The metrics used where: 
\begin{enumerate}

    \item Number of collisions
    The total amount of collisions between pedestrians.

    \item Total duration of collisions:
    The sum of the duration of each collision.

    \item Average walking speed:
    The average of the average speed of each pedestrian.

    \item Average travel time:
    The average time that a pedestrian needed unit it reached the goal.

    \item Average travel distance:
    The average distance that a pedestrian traveled unit it reached the
    goal.

    \item Average turn angle:
    The average angle turned by a pedestrian unit it reached the goal.

@@

\begin{itemize}

\item Pedestrian
\begin{itemize}
    \item $K_{1}=100$ {[}N/m{]}, 
    \item $\gamma=10$
    \item $K_{2}=150$ {[}N/m{]}
\end{itemize}

\item FVP-FVP interaction
    \begin{itemize}
        \item $\alpha=1000$
        \item $\beta=[0.4,\,0.5]$ (Uniform distribution)
    \end{itemize}

    \item Pedestrian-FVP interaction
    \begin{itemize}
        \item $\alpha=1000$
        \item $\beta=0.1$
    \end{itemize}

    \item FVP-Wall interaction
    \begin{itemize}
        \item $\alpha=10000$
        \item $\beta=0.1$
    \end{itemize}
\end{itemize}

@@

\begin{tabular}{|c|c|c|}
    \hline 
    Metric & {\scriptsize{FVPM}} & {\scriptsize{(SFM) $\alpha=2000,\,\beta=0.08$}}\tabularnewline
    \hline 
    \hline 
    $1$ & {\scriptsize{$(1.800,0.748)$}} & {\scriptsize{$(5.333,2.625)$}}\tabularnewline
    \hline 
    $2$ & {\scriptsize{$(34.600,8.333)$}} & {\scriptsize{$(12.333,8.340)$}}\tabularnewline
    \hline 
    $3$ & {\scriptsize{$(1.024,0.016)$}} & {\scriptsize{$(1.052,0.003)$}}\tabularnewline
    \hline 
    $4$ & {\scriptsize{$(1.910,0.022)$}} & {\scriptsize{$(1.876,0.003)$}}\tabularnewline
    \hline 
    $5$ & {\scriptsize{$(2.392,0.005)$}} & {\scriptsize{$(2.391,0.002)$}}\tabularnewline
    \hline 
    $6$ & {\scriptsize{$(91.062,12.122)$}} & {\scriptsize{$(106.185,13.778)$}}\tabularnewline
    \hline 
\end{tabular}

@@

@@

\newpage

\appendices

\section{Scenarios}
